How to Avoid OOTA Without Really Trying

### 2024-10-03 paper/ootavacuous.tex
ootavacuous: Flatten Section 7.5 list
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Additional future work could:
\begin{itemize}
\item	Extend these results to some classes of interpreters and JITs
	on one hand, and to link-time optimizations (LTO) on the other.
\item	Consider various classes of global analysis, such as
	demonstrating that a given expression will always evaluate
	to a constant.
\item	Examine the possibility of ``flattening'' optimizations that
	combine multiple threads into one.
\item	Explore cases in which semantic dependencies must be absolute,
	not relative to any particular compiler.
\item	Include the effects of input and output or other operations
	which can vary from one execution to another.
\item	Delineate more precisely the limits of permissible behavior
	for quasi-volatile object accesses.
\end{itemize}

>>>>

Additional future work could:
(1)~Extend these results to some classes of interpreters and JITs on
one hand, and to link-time optimizations (LTO) on the other;
(2)~Consider various classes of global analysis, such as
demonstrating that a given expression will always evaluate to a constant;
(3)~Examine the possibility of ``flattening'' optimizations that combine
multiple threads into one;
(4)~Explore cases in which semantic dependencies must be absolute,
not relative to any particular compiler;
(5)~Include the effects of input and output or other operations which
can vary from one execution to another; and
(6)~Delineate more precisely the limits of permissible behavior for
quasi-volatile object accesses.
